Predicting complex diseases: performance, robustness and ..utility..(impact?)

### 2017-11-23 3-simus.Rmd
save

### First simulations (with T-Trees)

@@

### Second simulations (without T-Trees, with logit-triple)

@@

### Third simulations (without logit-triple)

@@

### Fourth simulations (dataset with only chromosome 6)

@@

```{r, eval=FALSE}
if (!dir.exists("results4")) dir.create("results4")

@@

### Fifth simulations (varying training size)

>>>>

### Simulations n°1 (with T-Trees)

@@

### Simulations n°2 (without T-Trees, with logit-triple)

@@

### Simulations n°3 (without logit-triple)

@@

### Simulations n°4 (dataset with only chromosome 6)

@@

```{r, eval=TRUE}
if (!dir.exists("results4")) dir.create("results4")

@@

### Simulations n°5 (varying training size)

### 2017-11-23 paper/draft.tex
save

For simulations, we use real genotypes of European individuals from a case/control celiac disease cohort \cite[]{dubois2010multiple}. 
Details of quality control and imputation for this dataset are available in another study \cite[]{prive2017efficient}.
To get rid of the structure induced by the celiac disease status, we keep only controls from this cohort. Moreover, to get rid of population structure, we keep only people from UK and further subset these British people based on deviation of robust Mahalanobis distance on Principal Components (see ..SupMat..). This results in 7102 individuals genotyped on ..28x,xxx.. SNPs [ADD DIM TO RMD] with minimal population structure (see ..SupMat..). We decided to get rid of population structure because it can affect the predictive performance of methods, which we will investigate in another study.

@@

>>>>

We use real genotypes of European individuals from a case/control celiac disease cohort \cite[]{dubois2010multiple}. 
Details of quality control and imputation for this dataset are available in another study \cite[]{prive2017efficient}.
For simulations, in order to get rid of the structure induced by the celiac disease status, we keep only controls from this cohort. Moreover, to get rid of population structure, we keep only people from UK and further subset these British people based on deviation of robust Mahalanobis distance on Principal Components (see ..SupMat..). This results in 7102 individuals genotyped on ..28x,xxx.. SNPs [ADD DIM TO RMD] with minimal population structure (see ..SupMat..). We decided to get rid of population structure because it can affect the predictive performance of methods, which we will investigate in another study.

@@

\newpage
\begin{table}[htbp]
\caption{Summary of all simulations. When there is symbol `-' in a box, it means that the parameters are the same as the ones in the upper box.}
\vspace*{0.5em}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
Numero of & \multirow{2}{*}{Dataset} & Size of & Causal SNPs & Distribution & \multirow{2}{*}{Heritability} & Simulation & Number of & \multirow{2}{*}{Methods} \\ 
simulation & & training set & (number and location) & of effects & & model & simulations & \\
\hline
\hline
\multirow{4}{*}{1} & \multirow{4}{*}{All 22 chromosomes} & \multirow{4}{*}{6000} & 30 in HLA & \multirow{2.5}{*}{Gaussian} & \multirow{4}{*}{0.8} & \multirow{2.5}{*}{simple} & \multirow{4}{*}{5} & PRS \\
& & & 30 in all & & & & & logit-simple \\
& & & 300 in all & \multirow{1.5}{*}{Laplace} & & \multirow{1.5}{*}{fancy} & & logit-triple \\
& & & 3000 in all & & & & & T-Trees \\
\hline
\multirow{3}{*}{2} & \multirow{3}{*}{-} & \multirow{3}{*}{-} & \multirow{3}{*}{-} & \multirow{3}{*}{-} & \multirow{2}{*}{0.5} & \multirow{3}{*}{-} & \multirow{3}{*}{20} & PRS \\ 
& & & & & \multirow{2.2}{*}{0.8} & & & logit-simple \\
& & & & & & & & logit-triple \\
\hline
\multirow{2}{*}{3} & \multirow{2}{*}{-} & \multirow{2}{*}{-} & \multirow{2}{*}{-} & \multirow{2}{*}{-} & \multirow{2}{*}{-} & \multirow{2}{*}{simple} & \multirow{2}{*}{80} & PRS \\ 
& & & & & & & & logit-simple \\
\hline
\multirow{2}{*}{4} & \multirow{2}{*}{Chromosome 6 only} & \multirow{2}{*}{-} & \multirow{2}{*}{-} & \multirow{2}{*}{-} & \multirow{2}{*}{-} & \multirow{2}{*}{-} & \multirow{2}{*}{100} & \multirow{2}{*}{-} \\ 
& & & & & & & & \\
\hline
\multirow{5}{*}{5} & \multirow{5}{*}{All 22 chromosomes} & 1000 & \multirow{5}{*}{300 in all} & \multirow{5}{*}{-} & \multirow{5}{*}{-} & \multirow{5}{*}{-} & \multirow{5}{*}{100} & \multirow{5}{*}{-} \\ 
& & 2000 & & & & & & \\
& & 3000 & & & & & & \\
& & 4000 & & & & & & \\
& & 5000 & & & & & & \\
\hline
\end{tabular}
\label{}
\end{table}
